TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-24 paper/draft.tex
add ruwe cut figures
add met comparison figs

@@

\item \textbf{Astrometric cut:} \gaia\ $RUWE<1.2$

@@

\begin{figure*}[h]
	\includegraphics[width=.45\linewidth]{figures/cmd_teff_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_teff_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_feh_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_feh_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_spt_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_spt_safe.png}
	\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 5,875 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, spectroscopic binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence.}
	\label{fig:safe_selection}
\end{figure*}

@@

>>>>

\begin{figure*}
\begin{center}
	\includegraphics[width=.48\linewidth]{figures/ruwe_cut_before.png}
	\includegraphics[width=.48\linewidth]{figures/ruwe_cut_after.png}
	\caption{}
	\label{fig:ruwe_cut}
\end{center}
\end{figure*}

@@

\item \textbf{Astrometric cut:} \gaia\ re-normalised unit weight error (RUWE) $RUWE<1.2$

@@

\begin{figure*}[h]
\begin{center}
	\includegraphics[width=.45\linewidth]{figures/cmd_teff_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_teff_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_feh_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_feh_safe.png} \\
	\includegraphics[width=.45\linewidth]{figures/cmd_spt_full.png}
	\includegraphics[width=.49\linewidth]{figures/cmd_spt_safe.png}
	\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 5,875 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, spectroscopic binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence.}
	\label{fig:safe_selection}
\end{center}
\end{figure*}

@@

\begin{figure*}[h]
\begin{center}
	\includegraphics[width=5cm]{figures/met_comp1.png}
	\includegraphics[width=5cm]{figures/met_comp2.png}
	\includegraphics[width=5cm]{figures/met_comp3.png} 
	\includegraphics[width=5cm]{figures/met_comp4.png}
	\includegraphics[width=5cm]{figures/met_comp5.png}
	\includegraphics[width=5cm]{figures/met_comp6.png} 
	\includegraphics[width=5cm]{figures/met_comp7.png}
	\includegraphics[width=5cm]{figures/met_comp8.png}
	\includegraphics[width=5cm]{figures/met_comp9.png} 
	\caption{A comparison of ASPCAP and Cannon metallicities for 8,335 test sample sources separated into temperature bins of 100K. We see the scatter and metal-poor bias of ASPCAP metallicities clearly increases at decreasing temperatures.}
\end{center}
\end{figure*}
